---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library("badger")
```

# EZFragility: Epileptogenic Zone Localization Based on Fragility Index
```{r, echo = FALSE, results='asis', warning=FALSE, message=FALSE}
url <- "Jiefei-Wang/EZFragility"
cat(
	badge_devel(url, "blue"),
    badge_lifecycle("experimental"),
    badge_code_size(url),
    badge_last_commit(url),
    # badge_dependencies(),
	  "[![R-CMD-check](https://github.com/Jiefei-Wang/Fragility/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Jiefei-Wang/Fragility/actions/workflows/R-CMD-check.yaml)",
    "[![Codecov test coverage](https://codecov.io/gh/Jiefei-Wang/Fragility/graph/badge.svg)](https://app.codecov.io/gh/Jiefei-Wang/Fragility)"
)


```

To load the package
```r
devtools::load_all()
```

The package contains an example data. To see it, type
```r
pt01Epoch
```
For your test code, please consider creating a folder scripts and put your code there. This folder will be ignored by git.

## TODO:

- Exported function names and parameters to snake case(e.g. nSearch -> n_search)
- Unit test
- Vignette
- Check examples in the function documentation to make sure they are working
- Make sure all required functions/class have been exported
- Clear all error and warning in `devtools::check()` and `R CMD check --as-cran`
