---
title: "Introduction to EZFragility package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to EZFragility package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EZFragility)
```

This is the introduction to how to use the EZFragility package.
It calculates the neural fragility heatmap based on intracranial electrocorticographic (iEEG) recordings of ictal events.
The method is based on the paper by Li et al. (2017) <doi: 10.23919/ACC.2017.7963378>.
<a href="https://ieeexplore.ieee.org/document/7963378" style="color:blue; text-decoration:none;"> Fragility Method</a>

## Load small ictal ieeg data for patient PT01

This data corresponds to the first seizure of patient PT01 from the Fragility Data Set. The data contains only the good channels. It has been notch filtered and common average referenced in RAVE It has been epoched -3:5s around the seizure onset The acquisition frequency is 1000 Hz EcoG recording gathered in collaboration with the National Institute of Health. A Matrix with 8001 rows (time points) and 84 columns (electrodes). The columns names are the electrodes names. The row names is the time relative to seizure onset in (s)


```{r ictal data}
data("pt01Epoch")
# seizure onset (soz) electrodes indices
sozindex <- attr(pt01Epoch,"sozindex")
# seizure onset electrodes names
soznames <- attr(pt01Epoch,"soznames")

## Use data from -1s to 2s around the seizure onset
pt01Epochm1sp2s<-pt01Epoch[9001:12000,]
## Visualize ictal data
display <- c(sozindex,77:80)
time_window <- c(-1,2)
iEEGplot<-visu_iEEG_data(ieegts=pt01Epochm1sp2s,time_window=time_window,display=display)
iEEGplot
```


## Compute Fragility Matrix
Do not run if you are not ready to wait for >10 minutes. This is the non-optimized sequential version.
```{r compute fragility, eval=FALSE}
t_window <- 250
t_step <- 125
lambda <- NULL
n_search <- 10
pt01Fragm1sp2s <- calc_adj_frag(ieegts = pt01Epochm1sp2s, t_window = t_window, t_step = t_step, lambda = lambda,n_search=n_search)
# Fragility matrix result
pt01Fragm1sp2s$frag[1:5, 1:5]
```

## Plot a heatmap of the Fragility results for patient PT01 for soz electrodes and four non soz electrodes
This plot reproduces Patient 01 results Figure 4 a from Li et al. paper. Time window around seizure onset [-10:10]s
- `sozindex` contains the index of the soz electrodes
- `77:80` are the index of the non soz electrodes
```{r}
data("pt01Epoch")
sozindex<-attr(pt01Epoch,"sozindex")
data("pt01Frag")
time_window <- c(-10,10)
display <- c(sozindex,77:80)
fragplot<-heatmap_frag(frag=pt01Frag,elecsoz=sozindex,time_window = time_window,title="PT01 seizure 1",display=display)
fragplot
```

## Compute electrodes statistics of fragility map 
Compute quantiles, mean and standard deviation for two electrodes group marked as soz non marked as soz
```{r compute_frag_stat, eval=TRUE}
fragstat <- frag_stat(frag=pt01Frag, elecsoz=sozindex)
fragstat
```

## Plot Fragility distribution
Plot fragility distribution for two electrodes group marked as soz non marked as soz
```{r visualize_frag_auantile,out.width="100%"}
# plot the statistical results
pfragstat<-plot_frag_distribution(stat =fragstat,time_window=time_window)
pfragstat
```

## Plot fragility quantile
Plot Fragility quantiles for two electrodes group marked as soz non marked as soz
```{r visualize_frag_quantiles,out.width="100%"}
qfragplot<-plot_frag_quantile(qmatrix=fragstat, time_window=time_window)
qfragplot
```